Project 2

### 2021-10-03 project_2.Rmd
Adding project's code

This is an [R Markdown](http://rmarkdown.rstudio.com) Notebook. When you execute code within the notebook, the results appear beneath the code.

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*.

```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

>>>>

```{r load_libraries}
#loading all the necessary libraries
library(gutenbergr)
library(tidytext)
library(tidyverse)

```

```{r gutenberg_fitzgerald_works}
#finding texts by Fitzgerald on gutenberg
fitzgerald_text <- gutenberg_works(author == "Fitzgerald, F. Scott (Francis Scott)")
```

```{r gutenberg_fitzgerald_download}
#downloading all the texts found
fitzgerald_download <- fitzgerald_text %>% 
                      gutenberg_download(meta_fields = c("title", "author"))
```
